My wonderful paper

### 2024-08-01 _manuscript/_tex/index.tex
notes after the meeting

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

(background)

@@

describe/ define what analysis plan is

analysis plan and outcome plan

analysis plan as unit tests to divide the ``result universe'', which
allows us to answer questions like:

\begin{itemize}
\tightlist
\item
  how would the results change if the value of a unit test change
\item
  whether our outcome expectation aligns with the plan expectation,
  meaning whether ``it is possible for the combination of plan
  expectations to produce the outcome expectation''
\end{itemize}

@@

Figure~\ref{fig-result-universe} shows that result universe of the
linear regression model and how a change of decision in one of the plan
expectations above affect the outcome expectation. Panel a) is colored
by the outcome expectation -- whether a significant p-value is found in
the PM10 coefficient. Panel b) shows the effect of adding temperature to
the model and the results show that the significance of PM10 coefficient
can be achieved by adding temperature to the model for a sample size of
500. Panel c) shows that increasing sample size from 50 to 100 enhances
the significance of p-value for PM10 and the significance remains with
further increases in sample size.

A result universe constructed in this example can be presented to
analysts to answer the what-if questions raised in the data analysis.
What if the sample size is increased? What if temperature is added to
the model? What would the results expect to be changed when the
correlation structure is different? For analysts, expectations can be
used as unit tests to divide the result universe, which allows them to
understand the impact of each factor on the outcome expectation.

The result universe also provides a holistic view of how the results
obtained by the analysts are situated in all possible results. This can
be seen as a direct towards trustworthy data analysis, where the
audience of the analysis to exercise their own cognitive model
{[}@grolemund\_cognitive\_2014{]} to evaluate the results reported.

@@

\section{References}\label{references}

>>>>

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}

@@

{[}background{]}

@@

\begin{itemize}
\item
  describe/ define what analysis plan is, expectation (outcome and plan)
\item
  why it is useful to be explicit about expectation?

  \begin{itemize}
  \tightlist
  \item
    expectations can be used to formulate unit tests, which helps to
    divide the ``result universe''
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item
  add a paragraph to describe the simulation process
\item
  add a fourth panel to describe the comparison of a right/ wrong
  expectation, i.e.~correlation on PM10 and mortality
\end{itemize}

Figure~\ref{fig-result-universe} shows that result universe of the
linear regression model and how a change of decision in one of the plan
expectations above affect the outcome expectation. Panel a) is colored
by the outcome expectation -- whether a significant p-value is found in
the PM10 coefficient. Panel b) shows the effect of adding temperature to
the model and the results show that the significance of PM10 coefficient
can be achieved by adding temperature to the model for a sample size of
500. Panel c) shows that increasing sample size from 50 to 100 enhances
the significance of p-value for PM10 and the significance remains with
further increases in sample size. {[}note: weave the ``actual data''
into the example linear regression model{]}

(these two paragraphs may go to a new section \emph{discussion}) A
result universe constructed in this example can be presented to analysts
to answer the what-if questions raised in the data analysis. What if the
sample size is increased? What if temperature is added to the model?
What would the results expect to be changed when the correlation
structure is different? For analysts, expectations can be used as unit
tests to divide the result universe, which allows them to understand the
impact of each factor on the outcome expectation.

The result universe also provides a holistic view of how the results
obtained by the analysts are situated in all possible results. This can
be seen as a direct towards trustworthy data analysis, where the
audience of the analysis to exercise their own cognitive model
\citep{grolemund_cognitive_2014} to evaluate the results reported.

@@

\renewcommand\refname{References}
  \bibliography{references.bib}

### 2024-08-01 index.qmd
notes after the meeting

---
title: "My wonderful paper"
abstract: "This is the abstract"
#bibliography: references.bib
documentclass: jds
format: 
  pdf: 
   keep-tex: true
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
editor_options: 
  chunk_output_type: console
---

@@

(background)

@@

describe/ define what analysis plan is

analysis plan and outcome plan

analysis plan as unit tests to divide the "result universe", which allows us to answer questions like:

- how would the results change if the value of a unit test change
- whether our outcome expectation aligns with the plan expectation, meaning whether "it is possible for the combination of plan expectations to produce the outcome expectation"

@@

@fig-result-universe shows that result universe of the linear regression model and how a change of decision in one of the plan expectations above affect the outcome expectation. Panel a) is colored by the outcome expectation -- whether a significant p-value is found in the PM10 coefficient. Panel b) shows the effect of adding temperature to the model and the results show that the significance of PM10 coefficient can be achieved by adding temperature to the model for a sample size of 500. Panel c) shows that increasing sample size from 50 to 100 enhances the significance of p-value for PM10 and the significance remains with further increases in sample size.

A result universe constructed in this example can be presented to analysts to answer the what-if questions raised in the data analysis. What if the sample size is increased? What if temperature is added to the model? What would the results expect to be changed when the correlation structure is different? For analysts, expectations can be used as unit tests to divide the result universe, which allows them to understand the impact of each factor on the outcome expectation.

>>>>

---
title: "My wonderful paper"
abstract: "This is the abstract"
cite-method: natbib
bibliography: references.bib
documentclass: jds
format: 
  pdf: 
   keep-tex: true
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
editor_options: 
  chunk_output_type: console
---

@@

[background]

@@

* describe/ define what analysis plan is, expectation (outcome and plan)

* why it is useful to be explicit about expectation?

    * expectations can be used to formulate unit tests, which helps to divide the "result universe"

@@

 * add a paragraph to describe the simulation process

 * add a fourth panel to describe the comparison of a right/ wrong expectation, i.e. correlation on PM10 and mortality

@fig-result-universe shows that result universe of the linear regression model and how a change of decision in one of the plan expectations above affect the outcome expectation. Panel a) is colored by the outcome expectation -- whether a significant p-value is found in the PM10 coefficient. Panel b) shows the effect of adding temperature to the model and the results show that the significance of PM10 coefficient can be achieved by adding temperature to the model for a sample size of 500. Panel c) shows that increasing sample size from 50 to 100 enhances the significance of p-value for PM10 and the significance remains with further increases in sample size. [note: weave the "actual data" into the example linear regression model]

(these two paragraphs may go to a new section *discussion*) A result universe constructed in this example can be presented to analysts to answer the what-if questions raised in the data analysis. What if the sample size is increased? What if temperature is added to the model? What would the results expect to be changed when the correlation structure is different? For analysts, expectations can be used as unit tests to divide the result universe, which allows them to understand the impact of each factor on the outcome expectation.
